Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-09-23 ms.tex
added Gaia DR2 calculation.

\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data}.

>>>>

\added{We also confirm our finding that the star is a main sequence using the Gaia DR2 data.
The GAIA DR2 parallax of 618 $\pm$ 12 pc can be used with the bolometric flux and effective temperature to estimate the stellar radius \citep[e.g.][]{stassun2017gaiaRadiiMasses}.
We estimate a radius of 0.7 R$_\odot$, which is consistent with a main-sequence star.
}.
